|

### 2021-08-26 article/article.Rmd
main paper editing model and intro

Corruption is one of the most prevalent and harmful diseases of developing countries. Corruption lowers public goods provision \citep{banerjee201227, beekman2014corruption}, decreases foreign investments \citep{habib2002corruption}, stunt economic growth \citep{mauro1995corruption, grundler2019corruption}, and affects human capital investments \citep{ferraz2012corrupting}. Corruption also have detrimental effects on trust \citep{you2018trust}, attitudes toward political parties \citep{winters2015political}, and fuels the distrust in the political system \citep{mignozzetti2019brazil}. The International Transparency estimates that corruption is responsible for $1.23 trillion US dollars every year, a sum that could lift 1.4 billion people out of the extreme poverty for consecutive six years \citep{fleming2019corruption}.

One crucial distinction in corruption activity is the actor that is perpetrating corruption. While bureaucratic corruption may be more frequent, it is also easier to sanction and to punish. Political corruption, on the other hand, involves higher rents than bribes to services. They are usually associated with large government contracts and procurement \citep{broms2019political}, have a more disruptive effects on the trust in political institutions \citep{sole2018trust}, divert the bureaucracy toward rent seeking \citep{brierley2020unprincipled}. For instance, one of the major corruption scandals in the world, the Car Wash scandal in Brazil, involved more than 50 politicians, several high level bureaucrats, and about five billion US dollars in kickbacks \citep{watts2017operation}. Political corruption is intricate also because the electoral sanctioning often fails \citep{klavsnja2017uninformed, canete2020voting, janezic2020eliciting}. However, as elections are the primary mechanism to sanction corrupt politicians, are there electoral system features that could improve the sanctioning and lower corruption?

In this paper, I investigate the interplay between the number of incumbents in a polity, the number of competitors challenging those incumbents, and the incentives incumbents have for engaging in corruption. I propose a model where incumbents know the optimal level of investment required for public goods provision, but challengers only see the amount that incumbents spend. Incumbents have privileged information because they are inside the government, and receive information from governmental agencies. When they propose an investment higher than the optimal amount, the public goods is provided, and they pocket the difference between the optimal amount and their proposed expenditure. Thus, in this paper, the difference between the optimal and the proposed investment is the definition of political corruption.

Challengers have incomplete information about the required investment in public goods provision, but they may run a negative campaigning against incumbents. Challengers have a prior expectation regarding the optimal investments, and naturally, they know that the higher the level of investment proposed, the more the chances that incumbents are extracting rents. They decide to run a negative campaign that aims to gather and expose information supporting that a given incumbent is corrupt. To run a negative campaign is costly, both in terms of gathering information to prove that the incumbent is dishonest, and also in terms of XXXX. The extent through which the negative campaign is successful depends on the rents extracted by incumbents: While voters know that challengers may accuse an honest incumbent of corruption, the amount of evidence shown to voters can tilt the perception that a given incumbent is honest, triggering his or her dismissal.

To understand how electoral systems and competition affects corruption, I investigate how changes in the number of incumbents (district magnitude) and the number of challengers (competition) affect the equilibrium level of corruption. I show that increase district magnitude increases the equilibrium level of political corruption. This because more incumbents promote coordination failures in the challengers' negative campaigning. For example, in an electoral system with one incumbent, this incumbent is the sole target of negative campaigning. In a system with two incumbents, one incumbent may be targeted with all negative campaign while the other may remain un-targeted. These types of coordination shortcomings make the incumbents to propose higher expenditures, increasing corruption.

The effects of competition are less clear, and depend on the how voters behave in face of a successful exposure of an incumbent. On the one hand, if voters transfer the political support from the corrupt incumbent to the challenger that ran the negative campaign, then political corruption decreases. This because the reward in denouncing a corrupt incumbent makes challengers more prone to run negative campaigns. With more negative campaigning in equilibrium, incumbents respond by proposing an expenditure closer to the optimal spending level. On the other hand, if voters, upon being convinced that the incumbent is corrupt, decide to randomly elect one challenger, then political corruption increases. This because randomly select the challenger that substitute the corrupt incumbent creates a free-riding incentive: every challenger prefers that other challengers pay the cost of negative campaign. The first mechanism we denote as XXXX while the second mechanism we denote as XXXX.

This model innovates in three fronts. First, it provides a consistent and comparable definition of corruption. Despite the evidence that corruption is detrimental for XXXX and XXXX, corruption is poorly defined. Corruption XXXX. Moreover, corruption XXXX.

Second, our paper builds up on the previous literature on electoral systems and corruption by adding a role for the challengers. In most of the papers, XXXX. My paper innovates by XXXX.

Third, my model abstracts away from other political concerns, focusing only on features of the electoral system, in a stylized model. Recent papers show that corruption correlates with ideology \citep{XXXX}, in-group behavior \citep{XXXX}, and XXXX. Despite the importance of these XXXX, removing these considerations is fundamental for understanding how electoral rules affect corruption. For example, by having ideology and district size in the same model, we would be uncertain whether which component (or even if the interaction between them) leads to corruption. Moreover, high polarization correlates with less punishment of corruption \citep{XXXX}, but it is unrealistic to prescribe that voters should depolarize as a way to lower corruption. The relation between polarization, XXXX, and XXXX are features of the political system that need to be studied in and on themselves. The strength of my model is to abstract away from XXXX, and considering a lean model of XXXX.

Finally, XXXX

# District Magnitude, Competition, and Corruption

>>>>

Corruption is one of the most prevalent and harmful XXXX of developing countries. Corruption lowers public goods provision \citep{banerjee201227, beekman2014corruption}, decreases foreign investments \citep{habib2002corruption}, stunts economic growth \citep{mauro1995corruption, grundler2019corruption}, and affects human capital investments \citep{ferraz2012corrupting}. Corruption also has detrimental effects on interpersonal trust \citep{you2018trust}, attitudes toward political parties \citep{winters2015political}, and fuels the distrust in the political system \citep{mignozzetti2019brazil}. The International Transparency estimates that corruption is responsible for $1.23 trillion US dollars every year, a sum that could lift 1.4 billion people out of the extreme poverty for six consecutive years \citep{fleming2019corruption}.

One distinctive characteristic of corruption activity is the actor perpetrating corruption. While bureaucratic corruption may be more frequent, it is also easier to sanction and to punish. Political corruption, on the other hand, involves higher rents than bribes to access public services. Political corruption is associated with XXXX large government contracts and procurement \citep{broms2019political}, have a more disruptive effects on trust in political institutions \citep{rose2001trust, sole2018trust}, and divert the bureaucracy toward rent seeking \citep{brierley2020unprincipled}. For instance, one of the major corruption scandals in the world, the Car Wash scandal in Brazil, involved more than 50 politicians, several high level bureaucrats, and about five billion US dollars in kickbacks \citep{watts2017operation}. Given the XXXX of political corruption, it is essential to create mechanisms to sanction corrupt politicians involved in wrongdoings.

In democracies, elections are the primary mechanism to sanction politicians \citep{XXXX}. In most free and fair democracies, politicians can still manipulate XXXX, XXXX, and sometimes even the XXXX. This lowers the effectiveness of the XXXX. In this context, this paper XXXX.

However, many XXXX makes voters XXXX \citep{klavsnja2017uninformed, canete2020voting, janezic2020eliciting}.  , are there electoral system features that could improve the sanctioning and lower corruption? This paper studies the XXXX.

I investigate the interplay between the number of incumbents in a polity (electoral district sizes), the number of competitors challenging those incumbents (competitiveness), and the incentives incumbents have for engaging in corruption. I propose a model where incumbents know the optimal level of investment required for public goods provision, but challengers only see the amount that incumbents spend. Incumbents have privileged information because they are inside the government, and receive information from governmental agencies. When they propose an investment higher than the optimal amount, the public goods is provided, and they pocket the difference between the optimal amount and their proposed expenditure. Thus, in this paper, the difference between the optimal and the proposed investment is the definition of political corruption.

Challengers have incomplete information about the required investment in public goods provision, but they may decide to run a negative campaign against incumbents. Challengers have a prior expectation regarding the optimal investments, and they know that the higher the expenditure proposed, the more the chances that incumbents are extracting rents. They decide to run a negative campaign that aims to gather information supporting that a given incumbent is corrupt. To run a negative campaign is costly, both in terms of collecting information, and also in terms of opportunity costs of decreasing the focus on positive proposals \citep{haselmayer2019negative}. The extent through which the negative campaign is successful depends on the rents extracted by incumbents: While voters know that challengers may accuse an honest incumbent of corruption, the amount of evidence shown to voters can tilt the perception that a given incumbent is honest, triggering his or her dismissal.

By manipulate the parameters in the model, I show that increase district magnitude increases the equilibrium level of political corruption. This because more incumbents promote coordination failures in the challengers' negative campaigning. For example, in an electoral system with one incumbent, this incumbent is the sole target of all negative campaign. In a system with two incumbents, one incumbent may be targeted with all negative campaign while the other may receive no attacks. These coordination shortcomings make the incumbents to propose higher expenditures, increasing corruption.

The effects of competition are less straightforward, and depend on how voters behave in face of a successful incumbent exposure. I investigate two behavioral mechanisms: \textit{Excludable} versus \textit{non-excludable} negative campaigning. In the \textit{excludable} negative campaign, if voters transfer the political support from the corrupt incumbent to the challenger that ran the negative campaign, then the political corruption decreases. This because the reward in denouncing a corrupt incumbent makes challengers more prone to run negative campaigns. More challengers mean more negative campaigning in equilibrium, and incumbents respond by proposing expenditures closer to the optimal spending level. On the other hand, in the \textit{non-excludable} negative campaign if voters, upon being convinced that the incumbent is corrupt, decide to randomly elect one challenger, then political corruption increases. This because randomly select the challenger that substitute the corrupt incumbent creates a free-riding incentive: every challenger prefers that other challengers pay the cost of negative campaign.

This model innovates in four aspects. First, it provides a consistent and comparable definition of corruption. Despite the evidence that corruption is detrimental for countries, corruption is poorly defined. Studies have shown that there is wide variation, even within countries, in which acts are perceived as corruption \citep{peters1978political}. \citet{barr2010corruption} show that the propensity engage in corruption can be predicted by education and corruption in the country of origin. The variation is also pronounced in the willingness to punish corrupt behavior \citep{cameron2009propensities}. Despite the variability, reporting a higher than necessary cost of providing a public good seem to be overwhelmingly accepted as corruption \citep{peters1978political}.

Second, this paper builds on the literature on electoral systems and corruption by proposing a simple model of the trade-offs involved in electoral rules choices. : Number of seats and entry barriers.

Third, my model abstracts away from other political concerns, focusing only on features of the relationship between number of challengers and number of incumbents. Recent papers have shown that corruption correlates with ideology \citep{XXXX}, in-group behavior \citep{XXXX}, and XXXX. Despite the importance of these XXXX, removing these considerations is fundamental for understanding how electoral rules affect corruption. For example, by having ideology and district size in the same model, we would be uncertain about which component (or even if the interaction between them) leads to corruption. Moreover, high polarization correlates with less punishment of corruption \citep{XXXX}, but it is unrealistic to prescribe that voters should depolarize as a way to lower corruption. The relation between polarization, ideology, and or in-group sentiments are features of the society that need to be studied in and on themselves. The strength of my model is to abstract away from these concerns, and constructing a lean model of XXXX.

Finally, differences in the behavioral mechanism that voters use to reward challengers explain the empirical variations in corruption. In polities with widespread corruption, successfully exposing a corrupt politician have a small signaling effect \citep{pavao2018corruption}. This because the electorate considers the politician exposing the corrupt incumbent as as also corrupt. In these systems, increasing competition also increase the equilibrium corruption. Conversely, in countries with low corruption, voters may reward the politician exposing the corrupt incumbent. This creates an incentive for politicians to run negative campaigns, making incumbents to extract less rents in equilibrium.

# Electoral Rules and Corruption

XXXX

# Formal Model
\label{sec:theorymodel}

Consider a strategic interaction between three players: an incumbent politician ($I$), a challenger politician ($C$), and a representative voter ($V$).

The game starts in the \textit{governing stage}, with the incumbent deciding the governmental investment in public goods provision. Incumbents have a budget $R$ units, and they choose the level of investment in public goods between zero and $R$. To decide about the investment, they receive privileged information from governmental agencies about the optimal investment required to maximize voters' welfare. For example, if a politician is deciding the funding for a governmental agency, the optimal budget is the amount that makes the agency to function perfectly. Less resources than needed could decrease significantly the quality of services but more resources than needed would not improve the services much. In technical terms, the optimal amount of service provision is a random variable $\theta \in [0, R]$, that is drawn before the game starts, and it is informed to the incumbent after she wins the election. I assume that the optimal level of expenditure is drawn from a uniform probability distribution, with support in $[0, R]$.\footnote{In the online companion of this paper, I solve the model for a generic probability density function $f$.}

When deciding the expenditure, the incumbent can choose to invest more or less money then the optimal investment level. If the incumbent decide to invest less money, I assume that the goods are not provided. This simplification matches the reality in most cases, especially in developing economies, where restricting investments can cripple the entirety of the service provision. On the other hand, if the incumbent proposes an expenditure higher than the required investment, I assume that she pockets the difference between the proposed and the optimal expenditure. This has two implications: first, the public goods are always provided, satisfying the voters' needs; second, the incumbent has an excuse and a method to extract rents. Although corruption that ensures public goods provision seem counter-intuitive, the whole idea of kickbacks presumes that the expenditure is materialized. For instance, during the 2016 Brazilian World Cup, the stadiums constructed with public money were delivered, despite the fact that they costed 1.5 to 2.5 times more than comparable stadiums in less corrupt countries \citep{XXXX}.

After the governing stage, it starts the \textit{campaign stage}. During the campaign, the incumbent faces a challenger in an election with two characteristics. First, I assume that voters have a incumbent-bias, so that voters prefer to reelect incumbents for sure when the public good were successfully provided. This XXXX. Second, challengers have only one campaign instrument at their disposal: to use negative campaign against the incumbent, expose their malfeasance (if present), and XXXX.

Once in office, they learn the optimal public goods provision, but they have discretion to decide   is responsible for investing in public goods provision for the voters. For instance, XXXX.

XXXX, and proposes a public goods provision XXXX. The incumbent has a fixed budget of $A$ units, to invest in service provision. The level of expenditure required to provide the public goods is a random variable $\eta \in [0, A]$, where  The randomness reflects the idea that changes in real-world conditions influence the amount needed for service provision. The incumbent knows the optimal investment level, making it her private information. If incumbents were honest, they would invest the needed amount to provide the services ($\eta$), but in this model, the incumbent invests the optimal amount plus some value, that she intends to pocket. The utility from pocketing money is described by $u(e_i-\eta)$, which $u$ is a strictly concave utility function, and $e_i$ represents the service expenditure by an incumbent $i$.\footnote{This assumption matches a frequent empirical regularity in the political environment, especially in new democracies: corruption tend to be over-investments, meaning that politicians add kickbacks and gifts to procurement contracts, receiving benefits them. Usually, what happens is not that voters fail to receive the services, it is that those services cost much more than their market value. For instance, \citet{Bandiera2009} estimated that the waste in procurement account for around 2\% of the Italian GDP.}

After the service provision period, the electoral stage starts with the incumbent and the challenger campaigning. The challenger and the voters do not observe the optimal service investment level, but the challenger observes the amount of money invested by the incumbent politician ($e_i$, for all $i$). The challenger faces no entry costs and has the opportunity to use the negative campaign to convince the voters that the incumbent has embezzled public funds.\footnote{ This assumption is strong, as many papers demonstrated the effect of quality and service provision on the decision to challenge an incumbent \citep{Gordonetal2007, ashworth2008electoral, gordon2009voter, hall2015much}. In this paper, I endogenously fix the number of incumbents and challengers, as the critical point here is to study how the number of politicians influences incentives. In the Appendix, I extend the model to have a pool of possible challengers that have their entry costs a random variable. In the extension, the total pool of likely entrants becomes the critical variable, holding all qualitative findings here unchanged. Therefore, to fix the number of entrants is easier to understand, and represents a class of models that preserve the characteristics of our results, than we adopt this approach in the main text. Also, for the entry decision in economics, see \citet{Milgrom1982, Nti1989}.} If she decides to use all of her campaign resources to expose the corrupt politician, she pays a cost $c>0$. Her chances of success depend on the strength of the corruption evidence, plus other environmental facts, such as how much control over information incumbents have \citet{ferraz2011electoral, boas2011controlling}, credibility perceived by the voter \citep{polborn2006informative, AshworthShotts2011}, access to privileged information, and the challengers' competence to spread the information among voters. I assume that these factors are captured by a corruption detection technology, a function $\lambda(.)$ that is increasing on the amount embezzled by the incumbents. It increases with the amount embezzled, as the more money the incumbent pockets, the easier to convince voters that there is hard evidence of malfeasance undertaken by the incumbents.\footnote{There are two ways to interpret the hard evidence detection technology. First, it can be exposure of hard corruption evidence that was brought by a law enforcement agency, such as the FBI in the US or the General Comptroller Agency in Brazil. Second, it can be information uncovered during the campaign process by candidates or former allies that turned to the opposition. Either way, we consider that the process is noisy, but more substantial sums of money embezzled makes its detection easier.}

Finally, as the voters' decisions are sequentially rational, upon observing hard corruption evidence, they punish the incumbent electing the challenger. Otherwise, the claim that the incumbent is corrupt is interpreted as a cheap talk by the voters.\footnote{Note that it is not ex-ante rational to always dismiss (never dismiss) the politicians, even when the voters know that politicians are corrupt. This because always dismissing (never dismissing) would generate equilibrium where politicians always spend the total amount of resources, regardless of how much is needed to provide the services.} Thus, the voter only punishes the incumbent when the challenger presents and convinces the voters that there is hard evidence of malfeasance. The game then ends, and payoffs are realized. The timeline for this model is as follows:

\begin{enumerate}
 \item Nature draws the optimal investment level to provide the public services.
 \item The incumbent observes the optimal investment level and choose the expenditure.
 \item The election starts with the challenger choosing her campaign strategy.
 \item Voters observe the campaign and choose whether to retain or dismiss the incumbent.
\end{enumerate}

The strategic decisions in this game are the expenditure level chosen by the incumbent ($\varepsilon$), the fraction of time that the challenger invests in exposing the corrupt incumbent ($\varphi$), and the voter's decision to retain or dismiss the incumbent. Condensing the discussion above, we have the following expected utility functions. For the incumbents:

\[
U_i (\varepsilon_i; \ \eta, \ \bvphi^{*}, \ \bups^{*}, \ \varepsilon_{-i}^{*}) \ = \ u(\varepsilon_i - \eta) + B \ \Prob (\upsilon_i = 1 \ | \ \psi, \dd) 
\]

Where $B$ is the reward for staying in office (assumed the same for every player) and $\Prob (\upsilon_i = 1 \ | \ \psi, \dd)$ is the probability of being retained, given $\psi$ and the exposure profile $\dd$. For a challenger $j$:

\[
U_j (\bvphi_j; \ \bvphi^{*}_{-j}, \ \bups^{*}, \ \bveps^{*}) \ = \ B \int_{0}^A \Prob (\upsilon_j = 1 \ | \ \eta, \bveps^{*}, \bvphi^{*})\mu(\eta|\bveps^{*}) d\mu(\eta) - c \sum_{i=1}^K \varphi_{ij}(\psi, \bveps^{*})
\]

With $c > 0$ being the cost of performing one full corruption exposure. Notice that the total amount spent on exposing corrupt politicians will be the sum of the amounts spent on each exposure. The representative voter's expected utility is equal to:

\[
U_V (\psi, \dd, \bups) \ = \ \indf \{\psi=G \}r_G
\]

Where $\indf$ is the indicator function for $\psi=G$ and $r_G$ the value of the public good for the voter. Notice that no $\psi=B$ is observed on the equilibrium path, as under-spending is a dominated strategy.

Any retention rule selected for the voters is sequentially rational because there is no uncertainty about the results when they cast their votes. I impose the retention rule for the voter to be to dismiss all incumbents when $\psi=B$ or replace incumbents that were successfully exposed by challengers when $\psi=G$. This rule is ex-post efficient as over-dismissal would make incumbents pocket all the money regardless of $\eta$.

I solve this game for a \textit{Perfect Bayesian Equilibrium} \citep{Fudenberg1991book, Fudenberg1991}, and as this is a signaling game, I also use \textit{universal divinity} as the equilibrium selection criteria \citep{BanksSobel1987}.\footnote{The restriction imposed by the universal divinity requires that the challengers, facing a deviation from the equilibrium path, put probability one on the type that is more likely to deviate. Moreover, as we have a continuum of types, we use the approach by \citet{Malaith1987}, which consists in finding the monotonicity in the payoffs and single crossing conditions, characterizing the behavior of the types inside the intervals of the type space, analyzing the incentives to pool or separate among the types.}

\begin{definition}
 \label{def_eqn}
 A Perfect Bayesian Equilibrium for the game described, with $|I|=K$ and $|C|=L$, $K$ and $L$ in $\mathbb{N}$, type space $T=[0,A]$, consists in optimal strategies $\bveps^{*}$, $\bvphi^{*}$, $\bups^{*}$ and beliefs $\mu^*$, that satisfy
 \begin{enumerate}
  \item $\forall t_i \in T$, $\varepsilon^{*}_i(t_i)$ maximizes $ U_i (\varepsilon_i; \ t_i, \ \bvphi^{*}, \ \bups^{*}, \ \varepsilon_{-i}^{*}) $ $\forall i \in \{1, \cdots, K\}$.
  \item $\forall \bveps \in \left[0,A \right]^K $ and $\psi \in \{B, \ G \}$, $\bvphi^{*}_j(\bveps, \psi)$ maximizes $ U_j (\bvphi_j; \ \bvphi^{*}_{-j}, \ \bups^{*}, \ \bveps^{*}, \ \mu^*) $, $\forall j \in \{1, \cdots, L\}$
  \item $\forall \psi \in \{B, \ G \}$ and $\dd \in \{0,1\}^L$, $\bups^{*}(\psi, \dd)$ maximizes $ U_V (\psi, \dd, \bups^*) $.
  \item The beliefs are derived using Bayes rule whenever possible, and for all $\varepsilon_i$ that are off-the-equilibrium path, $\mu^*(t_i| \varepsilon_i)>0$ (in fact, 1) only if $\widehat{\varepsilon}_i \in \arg \min_{t_i} p(t_i, \widehat{\varepsilon}_i)$, where $ p(t_i, \widehat{\varepsilon}_i)$ is the profit from deviating from $\varepsilon_i$ to $\tilde{\varepsilon}_i$ for a type $t_i$.
 \end{enumerate}
\end{definition}

Note four characteristics of the model proposed. First, the incumbent politicians always embezzle some amount in equilibrium. Second, conditional on the benefits from holding office, to spend less than the optimal investment is harmful to the incumbent. In concrete terms, this means that politicians' first aim is to be elected. If the voter always dismisses the politician, then the politician will always say that the good costs $A$. Third, the voters always receive the public goods, regardless of the amount of money embezzled. The voter decides to punish the corrupt incumbent to discipline the incumbent's behavior, minimizing the rents extracted. Finally, this model has no ideological proximity, or affinity between the voter and any of the politicians: the paper aims to explore the incentives for corruption, not the trade-offs between ideology and corruption. Ideology is vital to understand why voters may not want to punish a corrupt politician, but this is not the main point of this paper, and adding this to the paper only blurs the logic of the argument. I now solve the model for the scenarios relevant to this paper.

\subsection{One incumbent and one challenger}

Applying backward induction, the voters retain the incumbent if the policy result was good and no corruption was exposed. From the challenger's perspective, as there is no cost of entry, she decides whether to invest or not her campaign resources in exposing the incumbent. She does so when the expected utility of exposing is higher than or equal the expected utility of not exposing, given her beliefs about the real value of $\eta$. Thus:

\[
B \int_{t_i \in T} \Prob (\bups = (0,1)\ | \ \eta, \varepsilon^*, \varphi)\mu^*(t_i|\varepsilon^*) d\mu - c \varphi(\psi, \varepsilon^*) \geq 0
\]

Rearranging and applying the fact that $ \Prob(\bups = (0,1) | \varepsilon^*, \varphi ( \psi, \varepsilon^*), \eta) = \varphi(\psi, \varepsilon^*) \lambda(\varepsilon^*-\eta) $ and $\mu^*(t_i | \varepsilon^*) = \mu(\eta) = \dfrac{f(\eta)}{\int_0^{A}f(\eta)d\eta}$ yields to:

\[
B \varphi(\psi, \varepsilon^*) \int_0^A \lambda(\varepsilon^* - \eta) \dfrac{f(\eta)}{\int_0^{A}f(\eta)d\eta} d\eta - c \varphi(\psi, \varepsilon^*)
\]

Isolating $\varphi(\psi, \varepsilon^*)$, let $\lambda_\varepsilon = \int_0^A \lambda(\varepsilon^* - \eta) \dfrac{f(\eta)}{\int_0^{A}f(\eta)d\eta} d\eta$ and $Q(B, c) = \dfrac{c}{B}$. Sequential rationality implies three distinct decisions: first, the challenger exposes the corrupt incumbent for sure whenever $\lambda_\varepsilon > Q(B, c)$; second, the challenger never exposes the corrupt incumbent when $ \lambda_\varepsilon < Q(B, c)$; and finally, the challenger is indifferent between exposing or not the corrupt incumbent when $\lambda_\varepsilon = Q(B, c)$. Optimality suggests that incumbent politicians will calibrate their rent extraction in order to make challengers indifferent between investigating or not.\footnote{To avoid a trivial equilibrium we assume that $Q < \dfrac{\int_0^A \lambda(A - \eta)f(\eta) d\eta}{\int_0^Af(\eta)d\eta} = Q^*$. If $Q \geq Q^*$, then the only equilibrium is to play $A$ regardless of $\eta$, and there will be no exposures.}

In this situation, there exists $\overline{\eta}$ such that:

\[
\lambda_A = \dfrac{\int_{\overline{\eta}}^A \lambda(A - \eta)f(\eta) d\eta}{\int_{\overline{\eta}}^Af(\eta)d\eta} = Q(B, c)
\]

This equation represents the upper limit in the incumbent politician's strategy when the randomly drawn optimal expenditure is too close to the maximum expenditure. In these situations is more profitable for them to play $A$. We say that the threshold for this case is $\overline{\eta}$.

Now, let $\delta(\varepsilon)$ the probability function that characterizes the amount of negative campaign chosen by the challenger when $\varepsilon \in [ 0, \ \overline{\eta}]$. The optimal $\varepsilon$ solves the equation $\lambda_\varepsilon = Q(B, c)$, making the challenger indifferent between exposing or not the incumbent's corruption. As $\lambda(.)$ has an inverse function, the optimal strategy for the incumbent is:

\begin{equation*}
\varepsilon^*(\eta) \ = \ \eta + \lambda^{-1}\left(\dfrac{c}{B}\right)
\end{equation*}

Therefore, the optimal strategy for the incumbent politician is to add a kickback $\kappa$ to the cost for providing the public good. The incumbent devises the optimal kickback to make the challenger indifferent between expose or not the corrupt incumbent. The optimal kickback is increasing in the cost of the negative campaign and decreasing in the benefit of holding office.

The incumbent, on the other hand, only plays this strategy when it is incentive compatible for her. To be an optimal response, it should be a $\arg \max$ for $U_I$. Taking the derivative of $U_I$, and setting it to zero gives us the following differential equation for $\delta(\varepsilon)$:

\[
\dfrac{d \delta}{d \varepsilon} + \delta(\varepsilon)\frac{\lambda^{'}(\kappa)}{\lambda(\kappa)} = \frac{1}{B}\frac{u^{'}(\kappa)}{\lambda(\kappa)}
\]

Under the boundary condition $\delta(\kappa)=0$. The equation is a well defined first order differential equation that has a straightforward unique solution determined by the boundary condition. Solving for $\delta(\varepsilon)$, we have:

\[
\delta(\varepsilon) = \dfrac{u^{'}(\kappa)}{B\lambda^{'}(\kappa)}\left(1 - e^{\frac{\lambda^{'}(\kappa)}{\lambda(\kappa)}(\kappa-\varepsilon)}\right)
\]

Combining all these results together gives us the following lemma:

\begin{lemma}
 \label{lemma_m1}
 A Perfect Bayesian Equilibrium for the game when there is one incumbent and one challenger is a pair of strategies and beliefs such that the optimal strategies are
 \begin{enumerate}
  \item For the incumbent 
  \[
   \varepsilon^{*}(\eta) \quad = \quad \twopd{\eta + \kappa}{0 \leq \eta \leq \overline{\eta}}{A}{\eta > \overline{\eta}}
  \]
  \item For the challenger
  \[
   \varphi^*(\varepsilon) \quad = \quad \threepdo{0}{\varepsilon < \kappa}{\delta(\varepsilon)}{\kappa \leq \varepsilon \leq \overline{\eta}}{\delta(A)}
  \]
 \item And the voter replaces the incumbent if there is evidence of corruption.
 \end{enumerate}
 Where $\lambda(.)$ is the challenger's campaign technology function. The optimal rent extraction is:
 \[
 \kappa = \lambda^{-1}\left(\dfrac{c}{B}\right)
 \]
 The upper threshold, $\overline{\eta}$, satisfies 
 \[
 \dfrac{\int_{\overline{\eta}}^A \lambda(A - \eta) f(\eta) d\eta}{\int_{\overline{\eta}}^A f(\eta)d\eta} - \dfrac{c}{B} = 0
 \]
 \[
 \delta(\varepsilon) \ = \ \dfrac{u^{'}(\kappa)}{B\lambda^{'}(\kappa)}\left(1 - e^{\frac{\lambda^{'}(\kappa)}{\lambda(\kappa)}(\kappa-\varepsilon)}\right) 
 \]
 And the beliefs are updated using Bayes rule whenever possible.
\end{lemma}

The remainder of the proof and the demonstration that this strategy is indeed an equilibrium is in the Appendix. Note three critical features on this equilibrium. First, an increase in the value of office ($B$) decreases the kickbacks extracted and the amount of negative campaign. Decreases kickbacks because it becomes more profitable to be reelected vis-a-vis extract rents, and lowers the amount of negative campaign because there are fewer opportunities to detect corrupt behavior. Second, increasing the costs of exposing corruption ($c$) increases the kickbacks and decreases the amount of exposure in equilibrium. Finally, increasing the gains from extracting rents (increasing $u'$) does not change the amount of extraction, but increases the amount of negative campaign, as a form to cope with the possibility of deviating from the equilibrium. These results are intuitive but demonstrate that the model follows a reasonable logic.
